
I would like to express gratitude towards the people without whom this thesis would not have been possible.

% - [ ] Olivier for a lot of feedback on my writing and providing an very good basis to work from
% - [ ] Francis for challenging my understanding of the research and bringing good new ideas to try when I was stuck.
First, I want to thank my counselor and advisor Olivier Pieters. 
The feedback he provided on the countless iterations of this book has been invaluable to the end product.
I wish to thank my promotor Francis wyffels for continuously challenging my understanding of my research results and coming up with new ideas to try when I felt like I reached a dead end.
I want to thank both of them especially for introducing me to the topic of reservoir computing.
It was certainly an unconventional pick from the list of dissertation topics, 
but every time I saw my peers struggle to stay interested in their subjects, I was glad I chose the unbeaten path.

% - [ ] Tom de swaef for explaining biological things and plant modelling concepts.
% - [ ] WUR/OnePlanet for the invitation to the meeting and tour of their phenotyping facility
% - [ ] Albasha for the feedback on the HydroShoot FSPM
I also want to thank Tom De Swaef for filling the gaps in my biological knowledge and helping me understand concepts in computer plant modeling.
Rami Albasha deserves a special mention for answering my questions about the inner workings of their grapevine simulation.
And thanks, Francis and OnePlanet Research Center, for inviting me to their research meeting.
Visiting WUR's phenotyping facilities and listening to their active projects helped me understand better how plant reservoir computing fits in the landscape of agricultural technology.

% - [ ] Jone & Tom for moral support, work group and sanity
% - [ ] Felix for moral support, sanity
Finally, I want to show gratitude to the people who have accompanied me during this arduous journey. 
Thank you to Jone Hoong and Tom for the social work sessions on Wednesdays and Thursdays at the iGent tower.
I admit I might have distracted you two more than I should have, but the weekly social interaction helped me stay sane as we slowly worked towards our finished thesis books.
My boyfriend Felix deserves a massive thank you for his patience when I worked late into the night and for listening to me vent my frustrations when progress was slow, or results were not as expected.
Last but not least, I want to thank my family for their patience when I was more distant and absent during this academic year.
I have always struggled to find the right balance between school and family, but now we can finally celebrate the end!


\vspace{0.5cm}

This dissertation topic challenged me to change my belief about what computation means.
After seven months of research, I hope that I can explain the concepts of plant reservoir computing to you in an accessible way. 
I believe that we are only at the beginning of the road for plant reservoir computing.
If the knowledge and technology can scale, I find the opportunities in agricultural tech immensely exciting.
