\chapter{Experimental Design} \label{chapter:exp-setup}

% Introduction
 Chapter \ref{chapter:lit-prc} established the necessary background on \acrshort{rc} and explained how physical media can function as a computational resource.
Then, Chapter \ref{chapter:fspm} introduced the rich research field of functional-structural plant modeling.
Now, we present how we will identify reservoir dynamics in plants and how we can quantitatively measure the reservoir performance, using simulated plants as the experiment subject.


\section{Reservoir Dynamics in Plants}
\input{sections/experimental-design/reservoir-dynamics-in-plants}


\section{Framework For Measuring Plant Reservoir Dynamics}
\input{sections/experimental-design/framework}


\section{Considered Reservoirs} \label{sec:considered-reservoirs}
\input{sections/experimental-design/model-requirements}


\section{Summary}

This chapter proposed a framework for quantitatively measuring reservoir characteristics of plant-physiological behavior.
In the first test, we use a suite of regression targets and a standard readout model to measure the capacity to perform nonlinear tasks.
% The predicted series is compared to the ground truth using the \acrshort{nmse} metric.
The second test investigates the fading memory property in an experiment where a brief artificial stimulus is applied to the plant's environment.
% We measure how the plant dynamics restore to their original trajectory using a divergence measure based on \acrshort{nmse}.
For the considered reservoirs, we prefer observable physiological traits using contactless sensing technologies. 
Still, the selection of reservoirs shown in the results will depend on what is available in the selected plant models.

% - Briefly recap how we will qualitatively and quantitatively measure reservoir performance
% 	- input separation experiments
% 	- fading memory experiments
% - Briefly recap what specific requirements this needs of our plant models.


\input{tables/pieters2022_table_3_1}

\input{tables/pieters2022_table_4_1}