
\chapter{Physical Reservoir Computing} \label{chapter:lit-prc}

\section{Reservoir Computing} \label{section:rc}
\input{sections/prc/reservoir_computing} 

\section{Physical Reservoir Computing} \label{section:prc}
\input{sections/prc/physical_reservoir_computing} 

\section{The Echo State Property} \label{section:esp}
\input{sections/prc/echo_state_property}
\input{figures/input_fading_explainer}

\section{Time Scale of Reservoir Dynamics} \label{section:rc-time-scales}
\input{sections/prc/rc_time_scales} 

\section{Evaluating Reservoir Performance} \label{section:reservoir-eval}
\input{sections/prc/prc_properties}

\section{Simulation of Physical Reservoirs} \label{section:prc-simulation}
\input{sections/prc/prc_simulation}

\section{Summary} \label{section:prc-summary}

This chapter showed how physical reservoir computing outsources computation to physical dynamical systems.
This works thanks to the emergent computational qualities present in nonlinear dynamical behavior.
A simple linear readout function is used to transform the reservoir's state into a useful output.
In computer models, we can observe the reservoir state directly.
In physical implementations, we observe the reservoir using sensor data.

To perform useful computations, the reservoir must perform the suitable nonlinear transformations and convolutions to its inputs such that the problem becomes linear.
Another condition for \acrshort{prc} is a fading memory of past inputs; Fading memory is essential to performing deterministic computations.

To test whether a physical material is suitable for reservoir computing, we can design a suite of regression targets to quantify the reservoir's correlation with relevant computational tasks.
In addition, we proposed two types of experiments for testing the fading memory condition: one measures the dependence on initial conditions, and the other measures the stationarity of the reservoir dynamics in time.