
\chapter{Selected Plant Models} \label{chapter:models-used}

% Chapter introduction
For the reasons stated in Chapter \ref{chapter:exp-setup}, we conduct our experiments with \textit{in silico} plants.
This chapter starts with a set of formal requirements that plant simulations must meet for use in physical reservoir computing.
Then follows an overview of the FSPMs from the literature we have examined for use in this research.
Finally, we introduce the final selection of models and compare their traits and characteristics.


\section{Selection Criteria} \label{sec:model-selection-criteria}
\input{sections/used-models/model-selection-criteria}


\section{Related Work} \label{sec:models-considered}
\input{sections/used-models/models-considered}


\section{Selected Models} \label{sec:selected-models}
\input{sections/used-models/selected-models}

\section{Summary}

First, we formalized the selection criteria to choose which plant models are suited for our research.
We based these criteria on considerations from an \acrshort{rc}, a plant-physiological, and a practical perspective.
Next, we held a brief discussion of each \acrshort{fspm} we considered from the literature.
Then, we made a final selection of two models: HydroShoot and CN-Wheat.
We introduced the background of each model and gave its implementation details.
Finally, we summarized their properties relevant to our experiments: the environmental inputs, the available regression targets, and the observations that can be used as a reservoir.


\input{tables/simulation_inputs}
\input{tables/simulation_regression_tasks}
\input{tables/simulation_reservoirs}